---
title: "ARE 202C PS2"
author: "Charlotte Ambrozek and Emily McGlynn"
date: "April 17, 2018"
output: html_document
---

```{r setup, include=FALSE, message = FALSE}
library(knitr)
library(tidyverse)
library(sjPlot)
library(MatchIt)
library(Zelig)
library(MatchItSE)
knitr::opts_chunk$set(echo = FALSE)
```

## 1

```{r q_1, include=FALSE, message= FALSE}
nic_rct <- read_csv("U:/Courses/202C/PS2/Nicaragua_RCT.csv")
subset_nic_rct <-  nic_rct[nic_rct$assign == 1,]

output_1 <- lm(income ~ complier, data = subset_nic_rct)

subset_nic_rct_2 <- mutate(subset_nic_rct, j1 = ifelse((job == 1),1,0), j2 = ifelse((job == 2),1,0), j3 = ifelse((job == 3),1,0), tj1 = (treat * j1), tj2 = (treat * j2), tj3 = (treat * j3))

output_2 <- lm(income ~ j2+j3+tj1+tj2+tj3, data = subset_nic_rct_2)

q1 <- sjt.lm(output_1, output_2, robust = TRUE)
```


Running the regressions again, we find $\hat{\beta}^{ATT} =$ `r output_1$coefficients[1]`, $\hat{\beta}_1^{ATT} =$ `r output_2$coefficients[4]`, $\hat{\beta}_2^{ATT} =$ `r output_2$coefficients[5]`, $\hat{\beta}_3^{ATT} =$ `r output_2$coefficients[6]`. These coefficients are larger than for the observations conditioned on $complier_i = 1$. This seems to indicate that when conditioning on individuals that request treatment, there is still some explanation of the treatment effect remaining in the error terms of equations (1) and (2). This could be explained by the fact that conditioning on compliance shows the difference between random assignment to treatment among individuals who all requested treatment, while conditioning on assignment shows the effect of treatment between anyone who requested treatment and was assigned treatment compared to those who were assigned treatment and did not request treatment. In this case, the bias from this selection effect is positive (treatment has a larger effect on income when not controlling for the effects of compliance/non-compliance). That is, we are more likely to be witnessing the effect of treatment across different "types" of people in the second regression, because we see both those who requested treatment and those that did not (who might reasonably be distinguished by ex ante income, capital, etc.).

`r q1`

## 2
```{r q_2, include=FALSE, message= FALSE}
output_3 <- lm(complier ~ age + education + capital + land + j2 + j3, data=subset_nic_rct_2)

q2 <- sjt.lm(output_3, digits.est = 4, digits.ci = 4)
```
We run a linear probability model for treatment, conditioning the data on $assign_i=1$, we regress complier on age, education, capital, land, job 2, and job 3. Each coefficient in this regression represents the marginal effect of that variable on the probability that $complier_i=1$. Thus for a positive coefficient there is evidence that, for example, as age increases, the probability of compliance being 1 increases.

The results of this regression indicate that none of the variables significantly influence compliance except for land. While the magnitude of the land effect is still small, it is significantly non-zero and positive. This is evidence that larger land holders are more likely to request treatment.

`r q2`

##3
```{r q_3, include=FALSE, message= FALSE, warning = FALSE}
output_4 <- glm(complier ~ age + education + capital + land + j2 + j3, data=subset_nic_rct_2, family=binomial(link="probit"))

#subset_nic_rct_3 <- mutate(subset_nic_rct_2, land_2 = land^2, land_3 = land^3, land_4 = land^4)
#output_5 <- glm(complier ~ age + education + capital + land + land_2 + j2 + j3, data=subset_nic_rct_3, family=binomial(link="probit"))

#output_6 <- glm(complier ~ age + education + capital + land + land_4 + j2 + j3, data=subset_nic_rct_3, family=binomial(link="probit"))

sjt.glm(output_4, exp.coef = FALSE, digits.est = 4, digits.ci = 4)

#subset_nic_rct_4 <- mutate(subset_nic_rct_3, pcomp_1 = fitted(output_4), pcomp_2 = fitted(output_5), pcomp_3 = fitted(output_6))


#q3_p1 <- plot(y = subset_nic_rct_4$land, x = subset_nic_rct_4$pcomp_1)
#q3_p2 <- plot(y = subset_nic_rct_4$land, x = subset_nic_rct_4$pcomp_2)
#q3_p3 <- plot(y = subset_nic_rct_4$land, x = subset_nic_rct_4$pcomp_3)
```

Again we find that land is the only variable with a significant effect on request for treatment. Notice that this is a probit model, wherein the model is fitting the data to a non-linear cumulative distribution function. Thus the probit coefficients don't have clear interpretations as marginal effects of right hand side variables on probability of compliance as in the linear model, so we can't interpret the same way we did in 2. 

##4
We posit that the answers to questions 2 and 3 provide statistically significant evidence that land holding size has an effect on likelihood of requesting treatment. The coefficients of land on expected compliance rate are significant across a number of model specifications, providing evidence of robustness. It is more difficult to say whether land holding size directly causes a larger likelihood of compliance or whether this variable is correlated with another, unobserved factor that is more directly attributable to a landowner's inclination to accept compliance. For example, large land owners may be more likely to be entrepreneurial, taking risks and interested in learning new information that can help their business. This likely has something to do with business savvy, high IQ, previous successes with experimentation, all of which could lead to higher land ownership.   

##5

```{r q_5, include=FALSE, message= FALSE, warning = FALSE}
income <- nic_rct$income
land <- nic_rct$land
cov <- cov(income, land)
cor <- cor(income, land)
```
Positing that land is the source of positive selection bias indicates the covariance of land and income would be positive - that is, we expect individuals with larger land holdings to also have higher income, and thus if larger land holding is correlated with request for treatment, we have a larger likelihood of treated individuals to have higher income ex ante, which biases our question of how treatment affects income. Looking at the data we see that in fact the correlation (and thus covariance) is positive, `r cor`. 

##6
````{r q_6, include=FALSE, message = FALSE}
output_7 <- lm(complier ~ age*j2 + age*j3 + education*j2 + education*j3 + capital*j2 + capital*j3 + land*j2 + land*j3, data=subset_nic_rct_2)
output_8 <- glm(complier ~ age*j2 + age*j3 + education*j2 + education*j3 + capital*j2 + capital*j3 + land*j2 + land*j3, data=subset_nic_rct_2, family=binomial(link="probit"))


q6 <- sjt.lm(output_7, output_8, robust = TRUE, p.numeric = TRUE)

xtabs(land~job,nic_rct)
```
Results from these models show that there is a small but significant negative effect of increasing land holdings on participation in treatment conditional on being a yucca or grain farmer (relative to cattle farmers). However, being a grain farmer *increases* likelihood of participation. As noted before, there is a small, significant positive effect of land holdings on participation.

The results lead us to believe that the land holding effects are driven by cattle farmers. Indeed, rerunning the results with grain farmers as the reference group rather than cattle farmers, we find that the land effect goes away and instead being a cattle farmer substantially decreases the likelihood of participation; however, conditional on being a cattle farmer, increasing land holdings further increases participation.

So we find some evidence of heterogeneity in the pattern of selection - probability of compliance moves in different directions as land holdings increase conditional on farmer type.

`r q6`

##7
```{r q_7, include=FALSE, message = FALSE, warning = FALSE}
subset_nic_rct_5 <-  nic_rct[nic_rct$assign == 1 & nic_rct$job == 1,]
subset_nic_rct_6 <-  nic_rct[nic_rct$assign == 1 & nic_rct$job == 2,]
subset_nic_rct_7 <-  nic_rct[nic_rct$assign == 1 & nic_rct$job == 3,]

lm_cattle_1 <- lm(income ~ complier + age + education + capital + land, data = subset_nic_rct_5)
lm_cattle_2 <- lm(income ~ complier + education + capital + land, data = subset_nic_rct_5)
lm_cattle_3 <- lm(income ~ complier + age + capital + land, data = subset_nic_rct_5)
lm_cattle_4 <- lm(income ~ complier + age + education + land, data = subset_nic_rct_5)
lm_cattle_5 <- lm(income ~ complier + age + education + capital, data = subset_nic_rct_5)

sjt.lm(lm_cattle_1, lm_cattle_2, lm_cattle_3, lm_cattle_4, lm_cattle_5, show.header = TRUE, string.dv = "CATTLE", p.numeric = FALSE, show.ci = FALSE, digits.est = 4, digits.ci = 4)

lm_grain_1 <- lm(income ~ complier + age + education + capital + land, data = subset_nic_rct_6)
lm_grain_2 <- lm(income ~ complier + education + capital + land, data = subset_nic_rct_6)
lm_grain_3 <- lm(income ~ complier + age + capital + land, data = subset_nic_rct_6)
lm_grain_4 <- lm(income ~ complier + age + education + land, data = subset_nic_rct_6)
lm_grain_5 <- lm(income ~ complier + age + education + capital, data = subset_nic_rct_6)

sjt.lm(lm_grain_1, lm_grain_2, lm_grain_3, lm_grain_4, lm_grain_5, show.header = TRUE, string.dv = "GRAIN", p.numeric = FALSE, show.ci = FALSE, digits.est = 4, digits.ci = 4)

lm_yucca_1 <- lm(income ~ complier + age + education + capital + land, data = subset_nic_rct_7)
lm_yucca_2 <- lm(income ~ complier + education + capital + land, data = subset_nic_rct_7)
lm_yucca_3 <- lm(income ~ complier + age + capital + land, data = subset_nic_rct_7)
lm_yucca_4 <- lm(income ~ complier + age + education + land, data = subset_nic_rct_7)
lm_yucca_5 <- lm(income ~ complier + age + education + capital, data = subset_nic_rct_7)

sjt.lm(lm_yucca_1, lm_yucca_2, lm_yucca_3, lm_yucca_4, lm_yucca_5, show.header = TRUE, string.dv = "YUCCA", p.numeric = FALSE, show.ci = FALSE, digits.est = 4, digits.ci = 4)

```
For yucca, omitting capital and land have the largest effects on the treatment coefficient. For grain, omitting education has the largest effect, followed by omitting capital and then land. For cattle, omitting land has a tremendous effect, tripling the coefficient on treatment. We note that cattle also has the largest number of observations - thus while land is not the largest contributor to selection bias for all types of farms, it has a huge effect for cattle ranchers, which form a majority of the observations. This is indeed consistent with what we have found in previous problems, that omitting land from the regression contributes to selection bias, yet here we see this is most problematic for cattle ranchers. 

##8
````{r q_8, include=FALSE, message = FALSE, warning = FALSE}
### Checklist of things to do:
#(1) estimate for each type of farmer (i.e. changing subset of data contingent on job)
#(2) for each type of farmer, drop controls one by one
#(3) change number of nearest neighbors (1, 5, 10, 15, 20 ,25)

att_fun <- function(farm, nn, controls, replace, n){
  frm <- paste("treat", controls, sep="~")
  mat <- matchit(formula(frm), data = subset_nic_rct[subset_nic_rct$job == farm,], replace = replace, ratio = nn, distance = "probit", method = "nearest")
  mat_dat <- match.data(mat)
  att_coef <- att(obj = mat, Y = subset_nic_rct[subset_nic_rct$job == farm,]$income)
  att_se <- abadie_imbens_se(obj = mat, Y = subset_nic_rct[subset_nic_rct$job == farm,]$income)
  att_ret <- data.frame(att_coef, att_se, farm, nn, controls, replace)
  return(att_ret)
}
args_r <- expand.grid( nn = c(1,5,10,15,20,25), farm = 1:3, controls = list("land + age + education + capital", "age + capital + education", "land + age + education", "land + age + capital", "land + education + capital"), replace = "TRUE")
args_dnr <- expand.grid( nn = c(1,5,10,15,20,25), farm = 1:3, controls = list("land + age + education + capital", "age + capital + education", "land + age + education", "land + age + capital", "land + education + capital"), replace = "FALSE")
att_r <- mapply(att_fun, nn = args_r$nn, farm = args_r$farm, controls = args_r$controls, replace = args_r$replace, SIMPLIFY = FALSE, USE.NAMES = TRUE) %>%
  bind_rows
att_dnr <- mapply(att_fun, nn = args_dnr$nn, farm = args_dnr$farm, controls = args_dnr$controls, replace = args_dnr$replace, SIMPLIFY = FALSE, USE.NAMES = TRUE) %>%
  bind_rows
q_8_a <- xtabs(att_coef~farm + controls, att_r)
q_8_b_1 <- xtabs(att_coef~farm + controls + nn, att_r)
q_8_b_2 <- xtabs(att_se~farm + controls + nn, att_r)
q_8_a_dnr <- xtabs(att_coef~farm + controls, att_dnr)
q_8_b_1_dnr <- xtabs(att_coef~farm + controls + nn, att_dnr)
q_8_b_2_dnr <- xtabs(att_se~farm + controls + nn, att_dnr)
#replace = list("TRUE", "FALSE"), 
#farm <- 1
#nn <- 5
#controls <- "land + age + education + capital"
#replace <- TRUE
```
### (A)
Our matching estimates of ATT vary across farm type but within farm type are more or less robust to systematic exclusion of controls with the exception of land for cattles farmers, for whom the estimate of ATT drops from about 700 to 1308. This is consistent from findings from question 6 in which we found that land holds effects on likelihood of treatment were mostly driven by cattle farmers.


### (B)
As the number of nearest neighbors increases, our point estimates of ATT increase away from the benchmark ATT estimates for the models "land education capital", "land age capital", and "land age capital education" (the change is less systematic for the models "land age education" and "age capital education"). However, we find evidence for a tradeoff between bias and precision, since the estimated standard errors of those point estimates decreases substantially as the number of nearest neighbors increases.

### (C)
The ATT is systematically higher than the ATE; this is likely due to the positive selection effect mentioned earlier in the problem set. Those individuals who choose to receive treatment have characteristics (like larger land holdings, or being a cattle farmer) that correspond with them receiving higher returns from the treatment than indivduals who do not choose to receive treatment, even if assigned to treatment. 

```{r junk, include=FALSE, message = FALSE, warning = FALSE}
#system: match_i_lace_n is the matching output for the subset of data where job == i and nearest neighbors == n, and controls are land, age, capital, and education respectively
  
subset_nic_rct_j1 <- subset_nic_rct[subset_nic_rct$job == 1,]
subset_nic_rct_j2 <- subset_nic_rct[subset_nic_rct$job == 2,]
subset_nic_rct_j3 <- subset_nic_rct[subset_nic_rct$job == 3,]

match_1_lace_1 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)
match_1_lac_1 <- matchit(treat ~ land + age + capital, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)
match_1_la_1 <- matchit(treat ~ land + age, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)
match_1_l_1 <- matchit(treat ~ land, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)

match_1_lace_5 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)
match_1_lac_5 <- matchit(treat ~ land + age + capital, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)
match_1_la_5 <- matchit(treat ~ land + age, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)
match_1_l_5 <- matchit(treat ~ land, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)

match_1_lace_10 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)
match_1_lac_10 <- matchit(treat ~ land + age + capital, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)
match_1_la_10 <- matchit(treat ~ land + age, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)
match_1_l_10 <- matchit(treat ~ land, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)

match_1_lace_25 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)
match_1_lac_25 <- matchit(treat ~ land + age + capital, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)
match_1_la_25 <- matchit(treat ~ land + age, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)
match_1_l_25 <- matchit(treat ~ land, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)

match_2_lace_1 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)
match_2_lac_1 <- matchit(treat ~ land + age + capital, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)
match_2_la_1 <- matchit(treat ~ land + age, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)
match_2_l_1 <- matchit(treat ~ land, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)

match_2_lace_5 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)
match_2_lac_5 <- matchit(treat ~ land + age + capital, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)
match_2_la_5 <- matchit(treat ~ land + age, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)
match_2_l_5 <- matchit(treat ~ land, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)

match_2_lace_10 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)
match_2_lac_10 <- matchit(treat ~ land + age + capital, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)
match_2_la_10 <- matchit(treat ~ land + age, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)
match_2_l_10 <- matchit(treat ~ land, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)

match_2_lace_25 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)
match_2_lac_25 <- matchit(treat ~ land + age + capital, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)
match_2_la_25 <- matchit(treat ~ land + age, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)
match_2_l_25 <- matchit(treat ~ land, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)

match_3_lace_1 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)
match_3_lac_1 <- matchit(treat ~ land + age + capital, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)
match_3_la_1 <- matchit(treat ~ land + age, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)
match_3_l_1 <- matchit(treat ~ land, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)

match_3_lace_5 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)
match_3_lac_5 <- matchit(treat ~ land + age + capital, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)
match_3_la_5 <- matchit(treat ~ land + age, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)
match_3_l_5 <- matchit(treat ~ land, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)

match_3_lace_10 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)
match_3_lac_10 <- matchit(treat ~ land + age + capital, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)
match_3_la_10 <- matchit(treat ~ land + age, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)
match_3_l_10 <- matchit(treat ~ land, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)

match_3_lace_25 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)
match_3_lac_25 <- matchit(treat ~ land + age + capital, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)
match_3_la_25 <- matchit(treat ~ land + age, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)
match_3_l_25 <- matchit(treat ~ land, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)

#Get ATT (only include treated group)
mat_dat_1_lace_1 <- match.data(match_1_lace_1, "treat") 
match_1_lac_1 <- matchit(treat ~ land + age + capital, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)
match_1_la_1 <- matchit(treat ~ land + age, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)
match_1_l_1 <- matchit(treat ~ land, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)

match_1_lace_5 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)
match_1_lac_5 <- matchit(treat ~ land + age + capital, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)
match_1_la_5 <- matchit(treat ~ land + age, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)
match_1_l_5 <- matchit(treat ~ land, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)

match_1_lace_10 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)
match_1_lac_10 <- matchit(treat ~ land + age + capital, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)
match_1_la_10 <- matchit(treat ~ land + age, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)
match_1_l_10 <- matchit(treat ~ land, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)

match_1_lace_25 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)
match_1_lac_25 <- matchit(treat ~ land + age + capital, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)
match_1_la_25 <- matchit(treat ~ land + age, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)
match_1_l_25 <- matchit(treat ~ land, subset_nic_rct_j1, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)

match_2_lace_1 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)
match_2_lac_1 <- matchit(treat ~ land + age + capital, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)
match_2_la_1 <- matchit(treat ~ land + age, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)
match_2_l_1 <- matchit(treat ~ land, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)

match_2_lace_5 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)
match_2_lac_5 <- matchit(treat ~ land + age + capital, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)
match_2_la_5 <- matchit(treat ~ land + age, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)
match_2_l_5 <- matchit(treat ~ land, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)

match_2_lace_10 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)
match_2_lac_10 <- matchit(treat ~ land + age + capital, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)
match_2_la_10 <- matchit(treat ~ land + age, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)
match_2_l_10 <- matchit(treat ~ land, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)

match_2_lace_25 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)
match_2_lac_25 <- matchit(treat ~ land + age + capital, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)
match_2_la_25 <- matchit(treat ~ land + age, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)
match_2_l_25 <- matchit(treat ~ land, subset_nic_rct_j2, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)

match_3_lace_1 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)
match_3_lac_1 <- matchit(treat ~ land + age + capital, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)
match_3_la_1 <- matchit(treat ~ land + age, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)
match_3_l_1 <- matchit(treat ~ land, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 1)

match_3_lace_5 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)
match_3_lac_5 <- matchit(treat ~ land + age + capital, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)
match_3_la_5 <- matchit(treat ~ land + age, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)
match_3_l_5 <- matchit(treat ~ land, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 5)

match_3_lace_10 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)
match_3_lac_10 <- matchit(treat ~ land + age + capital, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)
match_3_la_10 <- matchit(treat ~ land + age, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)
match_3_l_10 <- matchit(treat ~ land, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 10)

match_3_lace_25 <- matchit(treat ~ land + age + capital + education, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)
match_3_lac_25 <- matchit(treat ~ land + age + capital, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)
match_3_la_25 <- matchit(treat ~ land + age, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)
match_3_l_25 <- matchit(treat ~ land, subset_nic_rct_j3, distance = "probit", method = "nearest", replace = TRUE, ratio = 25)
```
