---
title: "AER 202C PS1"
author: "Charlotte Ambrozek and Emily McGlynn"
date: "April 5, 2018"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)
```

## 1
```{r data, include = FALSE}
nic_rct <- read.csv("U:/Courses/202C/PS1/Nicaragua_RCT.csv")
t_1 <- t.test(complier ~ assign, data = nic_rct, alternative = "two.sided")
mean_complier_assign0 <- t_1$estimate[1]
mean_complier_assign1 <- t_1$estimate[2]
t_stat_1 <- t_1$statistic[1]
p_val_1 <- t_1$p.value
```
If randomization is successful, then $E[complier_i|assign_i = 1]  = E[complier_i|assign_i = 0]$; that is, the probability of selecting into the program does not depend on assignment status. Thus we expect $E[complier_i|assign_i = 1]  - E[complier_i|assign_i = 0 ] = 0$ if randomization is successful.


The mean value of *complier* for treatment group households is `r mean_complier_assign1`; the mean value of *complier* for control group households is `r mean_complier_assign0`.


A two-sided differences of means t-test in Stata finds that the conditional means are not significantly different.


## 2
```{r test_2, include = FALSE}
varlist <- names(nic_rct)[4:9]
lapply(varlist, function(x){is.na(x)})

##### Now we know that there are no missing values in the data

output_2 <- sapply(varlist, function(x){
  frm <- paste(x, "assign", sep="~")
  t <- t.test(formula(frm), data = nic_rct, alternative = "two.sided")
  mean_0 <- t$estimate[1]
  mean_1 <- t$estimate[2]
  t_stat <- t$statistic
  p_val <- t$p.value
  t_df <- data.frame(mean_0 = mean_0, mean_1 = mean_1, t_stat = t_stat, p_val = p_val)
  return(t_df)
}, USE.NAMES = TRUE)

mean_income_1 = output_2[2,1]
mean_income_0 = output_2[1,1]
```

We also expect all control variables (*income, job, age, education, capital*, and *land*) to be uncorrelated with *assign* if randomization is successful.


There is some evidence that treatment households have higher incomes. The mean value of *income* for treatment group households is `r mean_income_1`; the mean value of *income* for control group households is `r mean_income_0`. A two-sided differences of means t-test (assuming unequal variances) in Stata rejects the null hypothesis that the conditional means are equal.

## 3
We belive income is not independent of household assignment status. This means that although assigment status and selection into treatment are independent, if we regress *income* on *treat* we will still come up with $\hat{\beta}$, a biased estimate of $\beta^{ATT}$. Notice that $treat_i = assign_i \times complier_i$.

Specifically, since $ATT = E[income_{1,i}|treat_i=1] - E[income_{0,i}|treat_i=1]$, and $E[\hat{\beta}] = E[income_{1,i}|treat_i = 1] - E[income_{0,i}|treat_i = 1] + E[income_{0,i}|treat_i = 1] - E[income_{0,i}|treat_i = 0]$ (with the middle two terms added and subtracted from the standard calculation of $E[\hat{\beta}]$), $\hat{\beta}$ is only unbiased for $\beta^{ATT}$ if $E[income_{0,i}|treat_i = 1] = E[income_{0,i}|treat_i = 0]$. 

```{r test_3, include=FALSE}
nicarag_2 <- select(filter(nic_rct, assign==1,treat==0), income)
nicarag_3 <- select(filter(nic_rct, assign==0), income)
t.test(nicarag_2, nicarag_3)
```
Testing the null hypothesis that mean income of assigned but untreated households is equal to mean income of unassigned and untreated households shows that this condition does not hold (p-value = 0.027), thus $\hat{\beta}$ is biased.  

## 4
```{r experiment_regression}
output_4 <- lm(income ~ assign, data = nic_rct)
beta_itt <- output_4$coefficients[2]
```

## 5

## 6
```{r subset_regression}
subset_nic_rct <-  nic_rct[nic_rct$assign != 0,]
```

## 7
```{r indicators}
subset_nic_rct <- as.tibble(subset_nic_rct)
subset_nic_rct <- mutate(subset_nic_rct, j1 = ifelse((job == 1),1,0), j2 = ifelse((job == 2),1,0), j3 =   ifelse((job == 3),1,0), tj1 = (treat * j1), tj2 = (treat * j2), tj3 = (treat * j3))

output_7 <- lm(income ~ tj1 + tj2 + tj3, data = subset_nic_rct)
```

## 8
