---
title: "AER 202C PS1"
author: "Charlotte Ambrozek and Emily McGlynn"
date: "April 5, 2018"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)
```

## 1
```{r data, include = FALSE}
nic_rct <- read.csv("U:/Courses/202C/PS1/Nicaragua_RCT.csv")
t.test(complier ~ assign, data = nic_rct, alternative = "two.sided")
```
If randomization is successful, then $E[complier_i|assign_i = 1]  = E[complier_i|assign_i = 0]$; that is, the probability of selecting into the program does not depend on assignment status. Thus we expect $E[complier_i|assign_i = 1]  - E[complier_i|assign_i = 0 ] = 0$ if randomization is successful.

The mean value of \textit{complier} for treatment group households is 0.5905325; the mean value of \textit{complier} for control group households is 0.6185936.

A two-sided differences of means t-test in Stata finds that the conditional means are not significantly different.


## 2

## 3

## 4

## 5

## 6

## 7

## 8