---
title: "ARE 202C PS2"
author: "Charlotte Ambrozek and Emily McGlynn"
date: "April 30, 2018"
output: html_document
---

```{r setup, include=FALSE, message = FALSE}
library(knitr)
library(tidyverse)
library(sjPlot)
library(systemfit)
### systemfit is also for simultaneous equations, but includes a SUR option
### systemfit seems to have more rigorous documentation behind it (i.e. pubs in journal of statistical software), let's use that one (sem is also an option)
library(alr3)
### for delta method
knitr::opts_chunk$set(echo = FALSE)
```

## 1

```{r q_1, include=FALSE, message= FALSE}
nic_rct <- read_csv("U:/Courses/202C/PS2/Nicaragua_RCT.csv")

itt_reg <- lm(income ~ assign, data = nic_rct)

beta_hat_itt <- itt_reg$coefficients[2]

subset_nic_rct <-  nic_rct[nic_rct$assign == 1,]

cond_expect_treat <- mean(subset_nic_rct$treat)

delta_hat <- beta_hat_itt/cond_expect_treat
```
The value of the estimator $\hat{\delta}$ is `r delta_hat`. The expectation of $\hat{\delta}$ is the average effect of treatment on the treated. If we assume constant treatment effects this is also the average treatment effect.

## 2
```{r q_2, include=FALSE, message= FALSE}
eqrf <- income ~ assign
eqfs <- treat ~ assign
syseq <- list(rf = eqrf, fs = eqfs)
IVSUR <- systemfit(syseq, method = "SUR", data = nic_rct)
IVSUR_sum <- summary(IVSUR)
beta <- IVSUR_sum$coefficients[2]
mu <- IVSUR_sum$coefficients[4]
delta_hat_2 <- beta/mu
vcov <- IVSUR_sum$coefCov[]
g <- as.vector(c(0, -beta*(mu^(-2)), 0, 1/mu))
### The jacobian of the transformation beta/mu is (0, 1/mu, 0, -beta/(mu^2))
#### Do delta method
dm <- (t(g)%*%solve(vcov)%*%g)^(0.5)
```
In order for $assign_i$ to serve as a valid instrument for $treat_i$ (allowing us to use the Wald IV estimator to recover the ATT), we require three assumptions:

1. Constant treatment effects

2. $cov(treat_i, assign_i) \neq 0$

3. $E[\epsilon_i | assign_i] = 0$

$\hat{\delta}$ is an example of a Wald IV estimator; with assignment as an instrument for treatment, we take the ratio of the coefficient from a regression of income on assignment to the coefficient of a regression of treatment on assignment.

Using seemingly unrelated regressions to estimate the system of simultaneous equations $income_i = \gamma + \beta^{ITT}\cdot assign_i +\epsilon_i$ and $treat_i = \lambda + \mu \cdot assign_i + \nu_i$ we can recover $\hat{\delta} = \frac{\beta^{ITT}}{\mu}$ with consistent standard error estimates despite the fact that there may be correlation across the disturbance terms $\epsilon_i$ and $\nu_i$. Notice that using seemingly unrelated regressions is an acceptable method since we assume that assignment is uncorrelated with all error terms (randomization was successful). We obtain a point estimate of `r delta_hat_2` for $\hat{\delta}$ with an estimated standard error of `r dm`.

## 3
```{r q_3, include=FALSE, message= FALSE, warning = FALSE}
att_reg_assign <- lm(income ~ treat, data = subset_nic_rct)
beta_hat_att_assign <- att_reg_assign$coefficients[2]
```
The estimate of $\hat{\beta}^{ATT}$ from the set of all complying households was 532.52; the estimate of $\hat{\beta}^{ATT}$ from the set of all assigned households was 925.69. We find that $\hat{\delta}$ is closer to the estimate from the subset of compliers. We expect that to be the case because households that were assigned to treatment may or may not have taken up the treatment. Thus the estimate from the subset of assigned households still includes the bias from selection into treatment, whereas the estimate from the subset of complying households does not. Our instrument, if valid, controls for the endogeneity between treatment and income captured by selection.

## 4
```{r q_4, include=FALSE, message= FALSE, warning = FALSE}
first_stage <- lm(treat ~ assign, data = nic_rct)
nic_rct <- mutate(nic_rct, treat_hat = fitted(first_stage))
man_tsls <- summary(lm(income ~ treat_hat, data = nic_rct))
beta_hat_man_tsls <- man_tsls$coefficients[2,1]
se_man_tsls <- man_tsls$coefficients[2,2]

tsls <- summary(systemfit(income~treat, method = "2SLS", inst = ~ assign, data = nic_rct))
beta_hat_tsls <- tsls$coefficients[2,1]
se_tsls <- tsls$coefficients[2,2]
```
The point estimate for $\hat{\beta}^{2sls}$ is identical to the estimate of $\hat{\delta}$ from the above questions (`r beta_hat_man_tsls` all around); however the standard error from manual 2SLS is `r se_man_tsls`, which is larger than the s.e. estimate from the Wald IV estimator `r dm`. This leads us to believe that manual 2SLS is *less* efficient than the Wald.

The point estimate from pre-packaged 2SLS is still on point at `r beta_hat_tsls`. Now the standard error estimate is lower than from manual 2SLS, as expected, but still larger than the Wald estimate. Since we computed the Wald estimate by hand using the delta method, there is likely user error in the Wald estimator of the standard error[^1].

[^1]: Stata's **nlcom** command with the Wald gives essentially an identical estimator to the standard error from tinned 2SLS - however, pre- and post-multiplying what we believe to be the Jacobian of the transformation by the variance-covariance matrix of the Wald coefficients didn't return the same thing. More insight about what Stata is doing better than us here would be helpful!

## 5

```{r q_5, include=FALSE, message= FALSE, warning = FALSE}
##Waiting on response from Kevin here
```

## 6
```{r q_6, include=FALSE, message = FALSE}
install.packages("AER")
library(AER)
install.packages("stargazer")
library(stargazer)
nic_rct <- mutate(nic_rct, j1 = ifelse((job == 1),1,0), j2 = ifelse((job == 2),1,0), j3 = ifelse((job == 3),1,0), tj1 = (treat * j1), tj2 = (treat * j2), tj3 = (treat * j3))

tsls_1 <- ivreg(income~treat|assign, data = nic_rct)
tsls_2 <- ivreg(income~treat + age|assign + age, data = nic_rct) 
tsls_3 <- ivreg(income~treat + age + capital |assign + age + capital, data = nic_rct)
tsls_4 <- ivreg(income~treat + age + capital + education |assign + age + capital + education, data = nic_rct)
tsls_5 <- ivreg(income~treat + age + capital + education + land|assign + age + capital + education + land, data = nic_rct)
tsls_6 <- ivreg(income~treat + age + capital + education + land + j1 + j2 + j3|assign + age + capital + education + land + j1 + j2 + j3, data = nic_rct) 
tsls_7 <- ivreg(income~treat + age + capital + education + land + j1 + j2 + j3 + tj1 + tj2 + tj3|assign + age + capital + education + land + j1 + j2 + j3 + tj1 + tj2 + tj3, data = nic_rct)

stargazer(tsls_1, tsls_2, tsls_3, tsls_4, tsls_5, tsls_6, tsls_7, column.sep.width = ".25pt", omit = "Constant", omit.stat = "all")

```

We find that as additional variables are included in the IV regression, the standard error of $\beta^{2sls}$ decreases, until the interaction terms between treatment and job type are included, then the point estimate of $\beta^{2sls}$ and the standard error sharply increases. Otherwise the estimate of treatment effect is fairly stable (the inclusion of land without the job dummies has the second largest effect on $\beta^{2sls}$, increasing the point estimate).

When including the control variables, we should now interpret $\beta^{2sls}$ as the average treatment effect on treated farms (and assuming constant treatment effects across farms, the average treatment effect), but *given* a specific set of controls - thus it should be interpreted as $ATT_x$ or $ATE_x$.  

## 7
```{r q_7, include=FALSE, message = FALSE, warning = FALSE}


```
$\beta^{2sls}$ will not be consistent for $\beta$ in this case because job type is controlled in both the first stage regression and in the main regression. Thus in the main regression $\beta^{2sls}$ will contain some information about the effect of job type on income, while the objective of the main regression is to identify the effect of treatment while holding job type constant. To isolate the effect of treatment holding job type constant, presumably it would make sense to either control for job type in either the first stage regression or second stage, but not both. 




```{r junk, include=FALSE, message = FALSE, warning = FALSE}
```
